---
title: "Trying Data Analyses"
output: html_notebook
---



### Overview
Learning r with data from camera trapping

Step One: Set up workspace
```{r}
rm(list = ls()) ## clear work space environment
library(tidyverse)
library(here)
library(lubridate)
```

Step Two: Pulling in data

```{r}
df<-read.csv(here("Data", "PostZooniverse", "AssignedSpecies_prebait_incomplete.csv"))
```

```{r}
ct_data<-read.csv(here("Data", "PostZooniverse", "cameratrapdata2021.csv"))
```

Let's summarize the data set and look for possible errors 

```{r}
summary(df)
```

Let's convert treatment to factor variable and the DTO to date time object (rather than character)

```{r}
#factor first
df$Treatment<- as.factor(df$Treatment)
df$DTO <- mdy_hm(df$DTO)

```
Notice the treatment column has multiple names for identifying Snapshot protocol so we need to fix. 

Treatment has three levels when should only have two. Need to fix!
```{r}
unique(df$Treatment)
levels(df$Treatment)
```

Changing all cams with "snap" to "snapshot"
To begin, find rows where treatment is "snap"

```{r}
fix<- which(df$Treatment == "Snap")
df$Treatment[fix]<- "Snapshot"
df$Treatment<- factor(df$Treatment)
levels(df$Treatment)
```




Let's look at how many species were detected


```{r}
num_species<- length(unique(df$choice))
species<- unique(df$choice)
species
```
Now we look at the number of each species as a function of treatment
- what data do we need? DF with species, treatment (AIM v snap)and number of events, need to group by and summarize

```{r}
species_sum<- df %>% group_by(choice, Treatment) %>% summarize(
  num_obs = length(choice)
)
```

Now we plot number of species as a function of treatment

```{r}
ggplot(species_sum, aes(choice, num_obs, fill = Treatment)) +
  geom_col(position = "dodge")+
  labs(y = "Number of observations")+
  coord_flip()
```
First, use `str_sub` to isolate camera num and sd num in df 
```{r}
df<-df %>% mutate(
  cam = str_sub(Img1, 3,4), 
  SD = str_sub(Img1, 9, 10),
  cam_SD = paste0(cam,"-", SD)
)
```

Now go to ct_data and do similar
```{r}
ct_data<-ct_data %>% mutate(
  cam = Camera_number, 
  SD = SD_num,
  cam_SD = paste0(cam, "-", SD)
)
```

Now we join the two data frames together 
```{r}
mydata<-left_join(df, ct_data, by = "cam_SD")
```

Now we calculate number of trap nights with newly combined data, have cam and sd on same with start and end date

```{r}
mydata$start_date<- dmy(mydata$start_date)
mydata$retrieval_date<- dmy(mydata$retrieval_date)
```

now calculate trap nights 
```{r}
mydata<- mydata %>% mutate(
  trap_nights = retrieval_date - start_date
)
```

Now we need to calculate observations per trap night 
everything in group by gets a column

```{r}
species_sum<- mydata %>% group_by(choice, cam_SD, Treatment) %>% summarize(
  num_obs = length(choice), 
  trap_nights = max(trap_nights))
```
now we balance to make across 100 nights 
```{r}
species_sum<- species_sum %>% mutate(
  obs_night = num_obs / as.numeric(trap_nights), 
  obs_100 = obs_night * 100
)
```


average per species between treatements 










Playing around with R 
```{r}
summary(species_sum)
```
```{r}
select(df, CamNum)
unique(df$CamNum)
```
 




