---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list = ls())
library(tidyverse)
library(lubridate)
library(here)
```

```{r}
species<- read.csv(here( "Data", "maggie_clean_species.csv"))
```
bringing in is there an animal
```{r}
is_there<- read.csv(here("Data", "Maggie_clean_is_there_species.csv"))
```


is there a difference in number of species detected between phase and treatment
can ask for how to make graph and stat test

need for statistic test for num species

```{r}
num_species<- species %>% group_by(Cam_SD, Phase, Treatment) %>% summarise(
  num_species = length(unique(choice))
)
```

now run stats
ANOVA 2way w interaction
```{r}
mspecies<- aov(num_species~ Phase + Treatment + Phase*Treatment, data = num_species)
summary(mspecies)
anova(mspecies)
```



for plotting need average 
T = true na.rm for saying to ignore NA
```{r}
avg_species<- num_species %>% group_by(Phase, Treatment) %>% summarise(
  avg_species = mean(num_species, na.rm = T), 
  sd_species = sd(num_species, na.rm = T)
)
```

now plot the data
+ creates new layer
```{r}
ggplot(avg_species, aes(Treatment, avg_species, group =Phase, color = Phase)) + 
  geom_line()+
  geom_point()+
  geom_errorbar(ymin = avg_species- sd_species, ymax = avg_species + sd_species)
```







Having trouble, not sure how to correct


trying to sort out data
```{r}
flse_trig<- length(unique(is_there$value))
```


making a table to compare aim and snap and is there
```{r}
#compare multiple columns 

df = is_there
combo_tabo<-table(df$Phase, df$Treatment, df$value)
phase<- as.factor(df$Phase)
treat<- as.factor(df$Treatment)
value<- as.factor(df$value)
combo_tabo
```

how do I split apart yes vs is there an animal?
breaking apart value colomn
```{r}
even separate(as.factor(value))

#moving on to more important
```


want to see how many false for AIM, problem is because of character I think and I am not sure how to go about that for species either. 
```{r}
falsify<- is_there %>% group_by(Phase, Treatment) %>% summarise(
  dont_see = sum(unique(value))
)
```


trying to run stats test on above table

```{r}
false_digs<- aov(as.factor(is_there)~ Phase + Treatment + value + Phase*value+ Phase*Treatment + Treatment*value, data = is_there)
summary(false_digs)
anova(false_digs)
```


finding if there is an animal or not
```{r}
there_compare<-is_there %>%  group_by(Phase, Treatment) %>%
  summarise(
    length(unique(is_there$value))
```
plotting if there is an animal or not 

```{r}
plot()
```

changing non integers to integers.

```{r}
is_there$Treatment<- as.factor(is_there$Treatment)

```




starting a new- sorry I haven't gotten further, a lot of trial and error 
```{r}
summary(avg_species)
```

